Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Final Draft - WiP}}

### 2014-12-06 Paper.tex
Empty Trie is the SHA3(rlp('')), not empty string.

We define the function $\texttt{\small TRIE}$, which evaluates to the root of the trie that represents this set when encoded in this structure. The empty trie is defined as being a the empty byte sequence, $()$:
\begin{equation}
\texttt{\small TRIE}(\mathfrak{I}) \equiv \begin{cases}
() & \text{if} \quad \mathfrak{I} = \varnothing \\
\texttt{\small KEC}(c(\mathfrak{I}, 0)) & \text{otherwise}
\end{cases}
\end{equation}

>>>>

We define the function $\texttt{\small TRIE}$, which evaluates to the root of the trie that represents this set when encoded in this structure:
\begin{equation}
\texttt{\small TRIE}(\mathfrak{I}) \equiv \texttt{\small KEC}(c(\mathfrak{I}, 0))
\end{equation}
